Videos Week 2 
========================================================

## Video 2
**bold**

- unordered list
- some list

[Some Link](http://www.google.com)

or some other link type

I spend some much time reading [R Bloggers][1] and [Simply Statistic][2]!
[1]: http://www.r-bloggers.com/ "R Bloggers" 
[2]: http://simplystatistics.org/ "Simply Stats"


## Video 3
### R Mark Down
The idea is it is a minimal document langauge that allows users to focus on the content and not worry about the formatting.

knitr evaluates the R code before making an HTML document. Markdown will not evaluate the R code.

you can write slides presentation in R markdown. You call slidify package to make presentation.

install.packages("slidify")


## Video 4
### Markdown Demonstration
```{r}
library(datasets)
data(airquality)
pairs(airquality)
```

```{r}
library(stats)
fit <- lm(Ozone ~ Wind + Solar.R + Temp, data = airquality)
summary(fit)

```

## Video 5
### Knitr PART 1
Weave doc to make human readable
Tangle to produce a computer code

**Pros**
- Text and code are in same spot
- Data results automatically update to reflect change
- code is live and is "regression test"

**Con**
- Text and code is in one place especially if there is a lot of code
- If lengthy processing time that will slow down rendering the document



## Video 6
### Knitr PART 2
Good for reports if you have to generate them periodically. You can generate new summary statistics

knitr is not good for:
- long research articles
- complex and time-consuming computations
- Documents that require precise formatting

## Video 7
### Knitr PART 3
My First knitr document
```{r ThisIsACodeChunkName}
myCodeChunk  <- 1
```

My First knitr document
```{r anotherCodeChunk, echo=FALSE}
myCodeChunk  <- 1
```


## Video 8
### Knitr PART 4
**knitr to HTML Process**  
.Rmd -> .md -> .html

**In Knitr you can calculate a value then later embed it in your text like this**  
```{r time, echo=FALSE}
time <- format(Sys.time(), "%a %b %d %X %Y")
```
The current time is **`r time`**. Note: this is an embedded calculated value in bold.

knitr embeds your plot as a base64 hex 


#### Set Global Options for Code Chunks
```{r setoptions, echo=FALSE}
## opts_chunk is a method in Rmarkdown that can be used to set global variables
opts_chunk$set(echo = FALSE, results = "hide")
```

First simulate data
```{r simulatedata, echo=TRUE}
x <- rnorm(100); y <- x + rnorm(100, sd = 0.5)
```
_Notice there is no results from this simulation here! They have been turned off_  
  
Here is a scatter plot of the data.

```{r scatterplot, fig.height=4}
par(mar = c(5,4,1,1), las = 1)
plot(x,y,main = "My Simulated Data")
```

**Cheat Sheet **
Output
- results: "asis", "hide" # AS IS means dont preprocess the results
- echo: TRUE, FALSE

Figures
- fig.height: numeric
- fig.width: numeric

####Caching Computations using knitr 
THis prevents knitr from having to recalulate the computations, it stores it on disk
```{r}
cache = TRUE
```



## Video 9
### Peer Assessment
Submit SHA-1 hash that describes the commit that is the final submission


## Assignment Notes

















